Language-Parametric Techniques for Live Probes

### 2023-08-04 paper/paper.tex
tweaks

\begin{table}[ht]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
  \hline
      \textbf{Line 3} & \textbf{Line 4} & \textbf{Line 5} & \textbf{Line 7} & \textbf{Line 8} \\ \hline
      n=3 & n=3;i=0 & n=3;i=0 & ~ & ~ \\ \hline
      ~ & n=3;i=1 & n=3;i=1 & ~ & ~ \\ \hline
      ~ & n=3;i=2 & n=3;i=2 & ~ & ~ \\ \hline
      ~ & n=3;i=3 & ~ & n=3;i=3 & return 3 \\ \hline
  \end{tabular}
  \label{tab:stack-recording}
  \caption{Stack Recording Example 2}
\end{table}

@@

\begin{table}[!ht]
  \centering
  \noindent\setlength\tabcolsep{4pt}%
  \begin{tabularx}{0.7\linewidth}{lc*{4}{>{\RaggedRight\arraybackslash}X}}
      \toprule
      Implementation & SLOC Live Probe Server & SLOC KAA \\
      \midrule
      Java JDI & 521 (Java) & 77 (Java) \\ 
      DAP Base & 267 (Python) & ~ \\ 
      DAP Python & 142 (Python) & 26(Python) \\ 
      DAP Java & 352 (Python) & 115 (Java) \\ 
      DAP Javascript & 257 (Python) & 24(Javascript) \\ 
      DAP C & 188 (Python) & 14(C) \\
      \bottomrule
  \end{tabularx}
  \caption{SLOC of the Live Probe Server and Keep Alive Agent}
  \label{tab:sloc}
\end{table}

>>>>

\begin{table}[t]
  \centering
  \includegraphics[width=\textwidth]{img/matrix.pdf}
  \caption{Tracking variable values across time and space}
\end{table}

% \begin{table}[ht]
%   \centering
%   \begin{tabular}{|c|c|c|c|c|}
%   \hline
%       \textbf{Line 3} & \textbf{Line 4} & \textbf{Line 5} & \textbf{Line 7} & \textbf{Line 8} \\ \hline
%       n=3 & n=3;i=0 & n=3;i=0 & ~ & ~ \\ \hline
%       ~ & n=3;i=1 & n=3;i=1 & ~ & ~ \\ \hline
%       ~ & n=3;i=2 & n=3;i=2 & ~ & ~ \\ \hline
%       ~ & n=3;i=3 & ~ & n=3;i=3 & return 3 \\ \hline
%   \end{tabular}
%   \label{tab:stack-recording}
%   \caption{Stack Recording Example 2}
% \end{table}

@@

\begin{table}[!ht]
  %\centering
  \noindent\setlength\tabcolsep{4pt}%
  \begin{tabular}{lrlrl}
      \toprule
      Implementation & \multicolumn{2}{l}{\#SLOC Probe Server} & \multicolumn{2}{l}{\#SLOC Keep-Alive Agent} \\
      \midrule
      Java JDI & 521 & Java & 77 & Java \\ 
      DAP Base & 267  & Python & --- & \\ 
      DAP Python & 142 & Python & 26 & Python \\ 
      DAP Java & 352 & Python & 115 & Java \\ 
      DAP Javascript & 257 & Python & 24 & Javascript \\ 
      DAP C & 188 & Python & 14 & C \\
      \bottomrule
  \end{tabular}
  \caption{Size of the language specific components in SLOC and their implementation languages.}
  \label{tab:sloc}
\end{table}
